---
title: "ICCs SEs CIs for CH results"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R function
```{r}
FisherZtoICC=function(alpha,sd,df){
  ICC = (exp(alpha)-1)/ (exp(alpha)+1) #Estimated ICC using inversion FishersZ function
  ICC_SE = sd*2*exp(alpha)/(1+exp(alpha))^2
  alphaCI = c(alpha-qt(0.975,4)*sd,alpha+qt(0.975,4)*sd) #Estimated 95% CI using alpha using t-distribution with df=4
  #Estimated 95% CI of ICC using 95% CI of alpha using inversion FishersZ function
  ICC_CI = c((exp(alphaCI[1])-1)/(exp(alphaCI[1])+1),(exp(alphaCI[2])-1)/(exp(alphaCI[2])+1)) 
  print(paste0("Estimated 95% CI for Fisher's Z correlation parameter =", round(alpha,3), " is ", list(round(alphaCI,3))))
  print(paste0("Estimated ICC for Fisher's Z correlation parameter =", alpha, " is ", round(ICC,3)))
  print(paste0("Estimated SE (delta method) of ICC =", round(ICC,3), " is ", list(round(ICC_SE,3))))
  print(paste0("Estimated 95% CI for ICC =", round(ICC,3), " is ",list(round(ICC_CI,3))))
}
```
# For analysis results under GEEMAEE
## transferring correlation parameters under fisher Z to ICC scale
## For average intervention effects model, 
```{r}

FisherZtoICC(alpha=0.448,sd = 0.1847,df=4)
FisherZtoICC(alpha=0.291,sd = 0.1442,df=4)

```
## For incremental intervention effects model, 

```{r}
FisherZtoICC(alpha=0.205,sd = 0.0982,df=4)
FisherZtoICC(alpha=0.105,sd = 0.1075,df=4)
```

## For extended incremental intervention effects model, 

```{r}
FisherZtoICC(alpha=0.241,sd = 0.1153,df=4)
FisherZtoICC(alpha=0.096,sd = 0.0495,df=4)
```
# For analysis results under GEEUEE
## For average intervention effects model, 
## transferring correlation parameters under fisher Z to ICC scale 
```{r}
FisherZtoICC(alpha=0.378,sd = 0.3207,df=4)
FisherZtoICC(alpha=0.207,sd = 0.1117,df=4)
```
## For incremental intervention effects model, 
```{r}
FisherZtoICC(alpha=0.171,sd = 0.0337,df=4)
FisherZtoICC(alpha=0.076,sd = 0.0548,df=4)
```
## For extended incremental intervention effects model, 
```{r}
FisherZtoICC(alpha=0.209,sd = 0.8075,df=4)
FisherZtoICC(alpha=0.070,sd = 0.2867,df=4)
```



